DRAFT: v7 \\ Vibration Characterisation of Strollers and\\ Cargo Bicycles for Transporting Infants\\ \vspace{2mm} \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\

### 2025-10-17 main.tex
Version 7 of the paper.

\title{
  DRAFT: v6 \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
}

@@

This paper addresses both comfort and potential health effects for infants. We
equipped five strollers and two cargo bicycles with inertial measurement units
(IMU) and carried out 67 experiments on different road surfaces and with
different travel speeds, using dummies representing 0, 3, and 9-month-old
infants. We assessed the data and derived results using ISO~2631-1 frequency
weightings and procedures. Given that ISO-2631-1 is neither validated for
children nor for lying postures, we also report unweighted results to assess
power spectrum and bandwidth. We investigated the influence of vehicle, seat,
body size, speed, and road surface and provided recommendations to users,
designers, and for future research.

@@

\subsection{Comfort Assessment}
%
ISO~2631-1 recommends using the magnitude of the weighted seat pan acceleration
3D vector for comfort assessment. Figures \ref{fig:comfort-stroller} and
\ref{fig:comfort-bicycle} plot RMS of the acceleration magnitude along with the
comfort indicators provided in the standard that are based on adults seated in
public transit for an unspecified duration. It must be emphasised that the
ISO~2631-1 comfort assessment was compiled for adults, with many warnings and
limitations, and may not be applicable for other contexts or populations, like
infants or older children. We also include a line representing cyclists'
discomfort threshold reported by Gao~et.~al~\cite{Gao2018}. It is important to
recognise that cyclists perched on a bicycle seat seem to tolerate higher
vibration amplitudes than the public transit riders who were surveyed for the
ISO ratings. This points to possible weakness in the ISO recommendations or to
other factors affecting cycling discomfort (e.g., the ability to stand on the
pedals to lower vibration to the body and the head).

>>>>

\title{
  DRAFT: v7 \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
}

@@

This paper provides measurements of vibration exerted on infant dummies in
strollers and cargo bicycles, which may be used as risk indicators for
discomfort or health effects. We equipped five strollers and two cargo bicycles
with inertial measurement units (IMU) and carried out 67 experiments on
different road surfaces and with different travel speeds, using dummies
representing 0, 3, and 9-month-old infants. We derived results using ISO~2631-1
frequency weightings and procedures to enable comparison with previous studies.
However, given that ISO~2631-1 is neither validated for children nor for lying
postures, we also report unweighted results to assess power spectrum and
bandwidth. We investigated the influence of vehicle, seat, body size, speed, and
road surface and provided recommendations to users, designers, and for future
research. Furthermore, as an example of how such measurements could be used for
assessing discomfort and health effects, we discuss these in the light of
thresholds suggested by ISO~2631-1 and Gao~et.~al~\cite{Gao2018}.

@@

\subsection{Comfort Assessment}
%
ISO~2631-1 recommends using the magnitude of the weighted seat pan acceleration
3D vector for comfort assessment. Figures \ref{fig:comfort-stroller} and
\ref{fig:comfort-bicycle} plot RMS of the acceleration magnitude along with the
comfort indicators provided in the standard that are based on adults seated in
public transit for an unspecified duration. It must be emphasised that the
ISO~2631-1 comfort assessment was compiled for adults, with many warnings and
limitations, and may not be applicable for other contexts or populations, like
infants or older children. We also include a line representing cyclists'
discomfort threshold reported by Gao~et.~al~\cite{Gao2018}. It is important to
recognise that cyclists perched on a bicycle seat seem to tolerate higher
vibration amplitudes than the public transit riders who were surveyed for the
ISO ratings. This points to possible weakness in or contradiction to the ISO
recommendations or to other factors affecting cycling discomfort (e.g., the
ability to stand on the pedals to lower vibration to the body and the head).
